Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-24 papers/B1555_EdgeOn/B1555_letter.tex
table format update. Model parameters not updated yet

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{lcccccc}
%%\tableline\tableline
SIE&		&		 &  \\
+Expdisk\\
\tableline\tableline
SIE& $x$		& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\
	&					&					&  (km/s)			&			&						\\
		&$-0.1883$ 	&$-0.1923$	&$93.74$ 			&$0.27$	& $105.5 \degr$   \\
\tableline
Expdisk	& $x$		& $y$		& $M_{tot} $					& $e$	& $\theta$	& $r_e$ \\
				&				&				& $(h^{-1}M_{\odot})$	&			&						&				\\
		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.40 \degr$& $0.20 ''$  \\  
\tableline\tableline
2-SIE\\
\tableline
Bulge& $x$				& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\  
			&					&					&  (km/s)			&			&						\\
						&$-0.1809$ 	&$-0.1702$& $81.67$ 					&$0.27$	& $97.71 \degr$   \\
\tableline
Disk\\
						&$-0.1592$ 	&$-0.1833$& $69.91$ 					&$0.83$	& $7.40 \degr$   \\
\tableline

\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Positions are offsets from component A measured in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}

>>>>

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{ccccccc}
%%\tableline\tableline
		&SIE+Expdisk& 2-SIE		   
\\
\tableline\tableline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$93.74$ &	$81.67$	  \\
$M_{tot} / \sigma_2$& $1.19\times 10^{10} $  &$69.91$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\tableline

\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Subscripts 1 and 2 represent bulge and disk components in each model respectively. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
\end{center}
\end{table}
